H52F-05H: Robust Adaptation to\\Multi-Scale Climate Variability

### 2018-12-04 slides-agu/presentation.tex
Update slides and add figure

\documentclass[
  10pt,     % set default generic font size
  handout   % ignores all the \pause commands
]{beamer}
\usetheme[block=fill]{metropolis}

@@

\title{H52F-05H: Robust Adaptation to\\Multi-Scale Climate Variability}
\subtitle{Toward Better Water Planning and Management in an Uncertain World I}
\date{19 October 2018}
\author{\alert{James Doss-Gollin}$^1$, David J. Farnham$^2$, Scott Steinschneider$^3$, Upmanu Lall$^1$}
\institute{$^1$: Columbia University Department of Earth and Environmental Engineering\\$^2$: Carnegie Institution for Science\\$^3$: Department of Biological and Environmental Engineering, Cornell University}
\titlegraphic{\hfill\includegraphics[height=1.25cm]{SeasCrown_blue.png}}

@@

% Use TIKZ
\input{tikz_setup.tex}

@@

% macros
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\makeatletter
\newcommand*{\etc}{%
    \@ifnextchar{.}%
        {etc}%
        {etc.\@\xspace}%
}
\makeatother

@@

\begin{frame}{NYC After Sandy \citep{CityofNewYork:2013uh}}
  \begin{columns}%[T]
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\columnwidth]{three-barriers.png}
        \caption{Possible construction of barriers for storm surge protection in New York}
      \end{figure}
      Structural ``Mega-Project'':
      \begin{itemize}
        \item Expensive: $\approx$ \$ 25 billion
        \item Environmental, social impacts
      \end{itemize}
    \end{column}
    \pause
    \begin{column}{0.5\textwidth}
      Alternative:
      \begin{itemize}
        \item Lots of local-scale projects
        \item Resilience boosting and vulnerability reduction
        \item Ecological restoration, financial instruments, zoning changes, structures where needed
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

\appendix
\renewcommand{\thefigure}{A\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\theequation}{A\arabic{equation}}
\setcounter{equation}{0}
\renewcommand{\thetable}{A\arabic{table}}
\setcounter{table}{0}
\section{Supplemental Figures}

\begin{frame}
  We can add more figures here
\end{frame}

>>>>

\documentclass[
  10pt,     % set default generic font size
  %handout   % ignores all the \pause commands
]{beamer}
\usetheme[block=fill]{metropolis}

@@

\title{H52F-05H: Robust Adaptation to\\Multi-Scale Climate Variability}
\subtitle{Toward Better Water Planning and Management in an Uncertain World I}
\date{19 October 2018}
\author{\alert{James Doss-Gollin}$^1$, David J. Farnham$^2$, Scott Steinschneider$^3$, Upmanu Lall$^1$}
\institute{
  $^1$Columbia University Department of Earth and Environmental Engineering\\
  $^2$Carnegie Institution for Science\\
  $^3$Department of Biological and Environmental Engineering, Cornell University}
\titlegraphic{\hfill\includegraphics[height=1.25cm]{SeasCrown_blue.png}}

@@

@@

% macros
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\makeatletter
\newcommand*{\etc}{%
    \@ifnextchar{.}%
        {etc}%
        {etc.\@\xspace}%
}
\makeatother
\newcommand{\usd}[1]{\SI[round-precision=2,round-mode=places,round-integer-to-decimal]{#1}[\$]{}}
\newcommand{\normal}{\mathcal{N}}

@@

\begin{frame}{NYC After Sandy \citep{CityofNewYork:2013uh}}
  \begin{columns}%[T]
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\columnwidth]{three-barriers.png}
      \end{figure}
      \begin{itemize}
        \item Environmental, social impacts
        \item Permanent and inflexible: $\mathcal{O} \qty(\$25 \text{billion})$ is ``locked-in''
        \item Potential for over- or under-design
      \end{itemize}
    \end{column}
    \pause
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\columnwidth]{flood-concept.png}
      \end{figure}
      \begin{itemize}
        \item Local resilience and vulnerability reduction
        \item Portfolio of long- and short-term investments
        \item Update portfolio regularly
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

\appendix
\renewcommand{\thefigure}{A\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\theequation}{A\arabic{equation}}
\setcounter{equation}{0}
\renewcommand{\thetable}{A\arabic{table}}
\setcounter{table}{0}

\section{Generating Synthetic Streamflow Sequences}

\begin{frame}{Equations for Synthetic Streamflow Generation}
  First
  \begin{equation} \label{eq:lognormal}
    \log Q(t) \sim \normal \qty(\mu(t), \sigma(t)).
  \end{equation}
  Where $\sigma(t) = \xi \mu(t)$, with $\sigma(t) \geq \sigma_\text{min} > 0$.
  Then,
  \begin{equation}\label{eq:nino3}
    \mu(t) = \mu_0 + \beta x(t) + \gamma \qty(t - t_0),
  \end{equation}
  and where $x(t)$ is NINO3.4 index from realistic ENSO model \citep{Zebiak:1987cl,Ramesh:2016hf}
\end{frame}

\begin{frame}{Spectrum of LFV Used}
  \begin{figure}
    \includegraphics[width=\textwidth,height=0.6\textheight,keepaspectratio=true]{enso_wavelet}
    \caption{Wavelet spectrum of (sub-set of) ENSO model used to embed synthetic streamflow sequences with low-frequency variability}
  \end{figure}
\end{frame}

\section{Climate Risk Estimation}

\begin{frame}{Stationary LN2 Model}
  Treat the $N$ historical observations as IID draws from stationary distribution
  \begin{align}\label{eq:ln2-stationary}
    \begin{split}
      \log Q_\text{hist} & \sim \normal \qty(\mu, \ \sigma) \\
      \mu &\sim \normal \qty(7, 1.5) \\
      \sigma &\sim \normal^+ \qty(1, 1)
    \end{split}
  \end{align}
  where $\normal$ denotes the normal distribution and $\normal^+$ denotes a half-normal distribution.
  Fit in Bayesian framework using stan \citep{Carpenter:2017ke}.
\end{frame}

\begin{frame}{Trend LN2 Model}
  Treat the $N$ historical observations as IID draws from log-normal distribution with linear trend
  \begin{align}\label{eq:ln2-trend}
    \begin{split}
      \mu &= \mu_0 + \beta_\mu \qty(t - t_0) \\
    \log Q_\text{hist} & \sim \normal \qty(\mu, \ \xi \mu) \\
    \mu_0 & \sim \normal \qty(7, 1.5) \\
    \beta_\mu & \sim \normal \qty(0, 0.1) \\
    \log \xi & \sim \normal \qty(0.1, 0.1)
    \end{split}
  \end{align}
  where $\xi$ is an estimated coefficient of variation.
  Also fit in stan.
\end{frame}

\begin{frame}{Hidden Markov Model}
  Two-state HMM \citep[see][]{Rabiner:1986jk} implemented using pomegranate python package \citep{Schreiber:2017tg}.
  See package documentation for reference.
\end{frame}
